Survival Compass

### 2024-04-18 paper/paper.qmd
playing around with some other figures in the results section

>>>>

# install.packages
# install.packages("reshape2")
# install.packages("vcd")

# Load required libraries
library(ggplot2)
library(arrow)
library(dplyr)
library(reshape2)
library(vcd)

# Create a contingency table
contingency_table <- table(analysis_data$pathologic_stage, 
                           analysis_data$presence_of_distant_metastasis, 
                           analysis_data$lymph_node_involvement, 
                           analysis_data$tumor_size, 
                           analysis_data$treatment_type)

# Plot mosaic plot for pathologic_stage and treatment_type with y-axis labels on the right side
mosaic(~pathologic_stage + treatment_type, data = analysis_data, shade = TRUE, labeling_args = list(rot_labels = c(90, 0)), gp = gpar(mar = c(5, 5, 5, 5)), split_vertical = TRUE)
